Precise predictions for same-sign W-boson scattering at the LHC

### 2018-02-26 Draft/conclusion.tex
minor typos fixed and small comments added in file conclusion.tex

As found in Ref.~\cite{Biedermann:2017bss}, the NLO EW corrections of order $\mathcal{O}{\left(\alpha^{7}\right)}$ are the dominant NLO contributions to the process $\Pp\Pp\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}\,\Pj\Pj+\mathrm{X}$.
It is thus highly desirable that they are combined with NLO-QCD predictions matched with parton shower.
In Ref.~\cite{Biedermann:2016yds}, it has been demonstrated that these large EW corrections originate from the Sudakov logarithms which factorise.
Therefore we recommend to combined them in a multiplicative way.
Concerning the estimation of missing higher-order corrections of EW type they can be obtained, in a first approximation, from $\pm \delta^2_{\rm NLO EW}$.
The missing higher-order mixed QCD-EW corrections can be estimate by taking the difference between the multiplicative and additive prescription.
A detailed study of the combination of higher-order corrections has been carried out e.g. in the context of top-pair production~\cite{Czakon:2017wor} or SM 
background for dark matter searches at the LHC \cite{Lindert:2017olm} and could be followed here as well.

@@

{\bf MZ there are many repetitions here}
Concerning predictions that include parton shower, we have shown that for observables defined at NLO, the differences are reasonable.
On the other hand, for observables only defined at NLO-QCD, such as the ones related to the third hardest jet, large differences can arise between different parton-shower algorithms.
Therefore, jet-veto procedures or selections based on extra radiation should be avoided as they carry rather large uncertainties.

@@

As demonstrated above, numerous programs exist to simulate the process $\Pp\Pp\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}\,\Pj\Pj+\mathrm{X}$ at the LHC.
So far there is no public code that perform the full NLO computation matched with parton shower.
Nonetheless, full computations at NLO and publicly available tools at NLO-QCD accuracy in the VBS approximation matched to parton shower are available.
Therefore, we encourage experimental collaborations to move to NLO accuracy supplemented with parton shower as much as possible.
In particular, we are willing to support this effort. \MP{Are we? - MZ: remove this sentence}

The present study has focused on the orders $\mathcal{O}{\left(\alpha^{6}\right)}$ at LO and $\mathcal{O}{\left(\alphas\alpha^{6}\right)}$ at NLO.
Nonetheless NLO computations and publicly available tools also exist for the QCD-induced process \cite{Rauch:2016pai,Melia:2010bm,Melia:2011gk,Campanario:2013gea,Baglio:2014uba,Biedermann:2017bss}.
They should therefore be also used as much as possible.

Uncertainties related to PDF has been hardly addressed in the present article.
{\bf MZ I would remove this and the following sentence: we computed PDF uncertainties,
    it is true that we did not comment much on it, but I think sayng 'Hardly addressed' is too much. I would anyway cite CS's proceedings when we
show the PDF uncertainties in the shower section}
It has only be discussed briefly in Sec.~\ref{sec:matching} where scale variation in combination with PDF variation has been shown.
Some of us have already presented preliminary results on this subject \cite{Schwan:2017yy}. % Radcor proceedings from Christopher.
Forthcoming publications will thus address related questions.

Finally, the study presented here concentrates on the ${\rm W}^+{\rm W}^+$ signature.
The features observed here (validity of the VBS approximation or comparison of theoretical predictions matched to parton shower for example) should be qualitatively similar for other VBS signatures with massive gauge bosons.
But the quantitative conclusions are strictly restricted to ${\rm W}^+{\rm W}^+$ signature.
For other signatures, similar quantitative study should be performed.
Beyond the theoretical findings of this work, we also hope that it can serve as a guideline for experimental collaborations in their quest for the measurements of VBS processes at the LHC.

>>>>

As found in Ref.~\cite{Biedermann:2017bss}, the NLO EW corrections of order $\mathcal{O}{\left(\alpha^{7}\right)}$ are the dominant NLO contributions to the process $\Pp\Pp\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}\,\Pj\Pj+\mathrm{X}$.
It is thus highly desirable that they are combined with NLO-QCD predictions matched with parton shower.
In Ref.~\cite{Biedermann:2016yds}, it has been demonstrated that these large EW corrections originate from the Sudakov logarithms which factorise.
Therefore we recommend to combine them in a multiplicative way.
Concerning the estimation of missing higher-order corrections of EW type they can be obtained, in a first approximation, from $\pm \delta^2_{\rm NLO EW}$.
The missing higher-order mixed QCD-EW corrections can be estimated by taking the difference between the multiplicative and additive prescription.
A detailed study of the combination of higher-order corrections has been carried out, e.g., in the context of top-pair production~\cite{Czakon:2017wor} or SM 
backgrounds for dark matter searches at the LHC \cite{Lindert:2017olm} and could be followed here as well.

@@

{\bf MZ there are many repetitions here} \BJ{I would suggest to remove the following paragraph as it repeats what was already said before.}
Concerning predictions that include parton shower, we have shown that for observables defined at NLO, the differences are reasonable.
On the other hand, for observables only defined at NLO-QCD, such as the ones related to the third hardest jet, large differences can arise between different parton-shower algorithms.
Therefore, jet-veto procedures or selections based on extra radiation should be avoided as they carry rather large uncertainties.

@@

As demonstrated above, numerous programs exist to simulate the process $\Pp\Pp\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}\,\Pj\Pj+\mathrm{X}$ at the LHC.
So far there is no public code that performs the full NLO computation matched with parton shower.
Nonetheless, full computations at NLO and publicly available tools at NLO-QCD accuracy in the VBS approximation matched to parton shower are available.
Therefore, we encourage experimental collaborations to move to NLO accuracy supplemented with parton shower as much as possible.
In particular, we are willing to support this effort. \MP{Are we? - MZ: remove this sentence}

The present study has focused on the orders $\mathcal{O}{\left(\alpha^{6}\right)}$ at LO and $\mathcal{O}{\left(\alphas\alpha^{6}\right)}$ at NLO.
Nonetheless, NLO computations and publicly available tools also exist for the QCD-induced process \cite{Rauch:2016pai,Melia:2010bm,Melia:2011gk,Campanario:2013gea,Baglio:2014uba,Biedermann:2017bss}.
They should therefore be also used as much as possible.

Uncertainties related to PDFs have been hardly addressed in the present article.
{\bf MZ I would remove this and the following sentence: we computed PDF uncertainties,
    it is true that we did not comment much on it, but I think sayng 'Hardly addressed' is too much. I would anyway cite CS's proceedings when we
show the PDF uncertainties in the shower section}
These have only been discussed briefly in Sec.~\ref{sec:matching} where scale variations in combination with PDF variations have been shown.
Some of us have already presented preliminary results on this subject \cite{Schwan:2017yy}. % Radcor proceedings from Christopher.
Forthcoming publications will thus address related questions.

Finally, the study presented here concentrates on the ${\rm W}^+{\rm W}^+$ signature.
The features observed here (validity of the VBS approximation or comparison of theoretical predictions matched to parton shower, for example) should be qualitatively similar for other VBS signatures with massive gauge bosons. \BJ{I am not sure this statement is generally true. For other VBS channels, backgrounds are much more troublesome. If we want to make a statement like ``qualitatively similar for other VBS signatures'' we need to say more explicitly in which respect, for instance concerning the validity of the VBS approximation.}
But the quantitative conclusions are strictly restricted to ${\rm W}^+{\rm W}^+$ signature.
For other signatures, similar quantitative studies should be performed.
Beyond the theoretical findings of this work, we also hope that it can serve as a guideline for experimental collaborations in their quest for the measurements of VBS processes at the LHC.
